\documentclass{article}
\setlength{\oddsidemargin}{0.25 in}
\setlength{\evensidemargin}{-0.25 in}
\setlength{\topmargin}{-0.6 in}
\setlength{\textwidth}{6.5 in}
\setlength{\textheight}{8.5 in}
\setlength{\headsep}{0.75 in}
\setlength{\parindent}{0 in}
\setlength{\parskip}{0.1 in}

% ===== PACKAGES =====
\usepackage{amsmath,amssymb}
\usepackage{color}
\usepackage{subfigure}
\usepackage{mdframed}
\usepackage{changepage}
\newmdenv[
  topline=false,
  bottomline=false,
  skipabove=\topsep,
  skipbelow=\topsep
]{siderules}
\renewcommand{\abstractname}{}

% ===== VARIABLES =====
\def \R{\mathbb{R}}
\def \Pr{\mathbb{P}}
\def \D{{\rm D}}
\def \N{{\rm N}}
\def \xx{{\boldsymbol{\rm x}}}
\def \y{{\rm y}}




% ===== HEADER BOX =====
\newcommand{\lecture}[2]{
\pagestyle{myheadings}
\thispagestyle{plain}
\newpage
\noindent
\begin{center}
\rule{\textwidth}{1.6pt}\vspace*{-\baselineskip}\vspace*{2pt} % Thick horizontal line
\rule{\textwidth}{0.4pt}\\[1\baselineskip] % Thin horizontal line
\vbox{\vspace{2mm}
\hbox to 6.28in { {\bf CS 760: Machine Learning} \hfill Spring 2024 }
\vspace{4mm}
\hbox to 6.28in { {\Large \hfill #1  \hfill} }
\vspace{4mm}
\hbox to 6.28in { {\scshape Authors:}  #2 \hfill }}
\vspace{-2mm}
\rule{\textwidth}{0.4pt}\vspace*{-\baselineskip}\vspace{3.2pt} % Thin horizontal line
\rule{\textwidth}{1.6pt}\\[\baselineskip] % Thick horizontal line
\end{center}
\vspace*{4mm}
}


% ===== Jed's Defined Stuff ======
\DeclareMathOperator*{\argmin}{arg\!\min}
\DeclareMathOperator*{\argmax}{arg\!\max}
\usepackage{siunitx}
\usepackage{enumitem} % used to make alphabetical lists instead of numbered ones
\usepackage{mathtools}

% =============== DOCUMENT ===============
\begin{document}
\lecture{Homework 4: Decision Trees}{Jed Pulley}

\begin{center}
{\Large {\sf \underline{\textbf{DO NOT POLLUTE!}} AVOID PRINTING, OR PRINT 2-SIDED MULTIPAGE.}}
\end{center}

\section*{Problem 4.1}
\textbf{Passenger Class:} First class is 1 and other classes are 0. \\
\textbf{Sex:} I left sex alone, since it was already binary. \\
\textbf{Age:} I split age based on the median. If you were above the median age, you get 0, otherwise 1. \\
\textbf{Siblings/Spouse:} I chose 1 for no siblings/spouses and 0 for any number of them. \\
\textbf{Parents/Children:} Similarly, I chose 1 for no parents/children and 0 for any \\
\textbf{Fare:} I split fare based on the median, if you are above, you get 1, otherwise 0.

\section*{Problem 4.2}
See $decision\_trees.ipynb$ under section 4.2 for code

\section*{Problem 4.3}
See $decision\_trees.ipynb$ under section 4.3 for code

Two variables, $max\_depth$ and $min\_samples\_split$, are defined as my  stopping conditions. If a node exceeds the max depth, then stop. Otherwise, if a node is about to be split more times than our minimum sample split, then it will stop as well. This prevents the tree from getting too deep or wide.

\section*{Problem 4.4}
See $decision\_trees.ipynb$ under section 4.4 for code

\section*{Problem 4.5}

\section*{Problem 4.6}

\section*{Problem 4.7}
\begin{enumerate}[label=(\alph*)]
  \item 
  \item 
  \item 
\end{enumerate}

\section*{Problem 4.8}
\begin{enumerate}[label=(\alph*)]
  \item 
  \item 
  \item 
\end{enumerate}

\section*{Problem 4.9}

\section*{Problem 4.10}

\end{document} 
































